---
title: "Agreement"
author: "Aaron R. Caldwell"
date: "5/5/2021"
output: pdf_document
editor_options: 
  chunk_output_type: console
---

```{r setup, include=FALSE,message=FALSE,warning=FALSE}
knitr::opts_chunk$set(echo = FALSE, warning=FALSE, message=FALSE)
source("agree_eval.R")
library(SimplyAgree)
```

# Hypothesis Tested

```{r }
df = data.frame(
  Journal = c(
    "EJSS",
    "JSAMS",
    "MSSE"
  ),
  Kappa = c(
  agree_na(df = df_ejss,
        cols1 = c("id","doi","hypo_tested"),
        spread1 = c("id"),
        spread2 = "hypo_tested",
        row1 = "doi")[[1]],
  agree_na(df = df_jsams,
        cols1 = c("id","doi","hypo_tested"),
        spread1 = c("id"),
        spread2 = "hypo_tested",
        row1 = "doi")[[1]],
  agree_na(df = df_msse,
        cols1 = c("id","doi","hypo_tested"),
        spread1 = c("id"),
        spread2 = "hypo_tested",
        row1 = "doi")[[1]]
),
  Observations = c(
  agree_na(df = df_ejss,
        cols1 = c("id","doi","hypo_tested"),
        spread1 = c("id"),
        spread2 = "hypo_tested",
        row1 = "doi")[[2]],
  agree_na(df = df_jsams,
        cols1 = c("id","doi","hypo_tested"),
        spread1 = c("id"),
        spread2 = "hypo_tested",
        row1 = "doi")[[2]],
  agree_na(df = df_msse,
        cols1 = c("id","doi","hypo_tested"),
        spread1 = c("id"),
        spread2 = "hypo_tested",
        row1 = "doi")[[2]]
))
df2 = df %>%
  mutate(Tot = Kappa * Observations)
knitr::kable(df)

```

Overall Agreement: `r round(sum(df2$Tot)/sum(df2$Observations),4)*100`%

# Number of Hypotheses

Continuous so switching to a intraclass correlation coefficient.

```{r}
df = data.frame(
  Journal = c(
    "EJSS",
    "JSAMS",
    "MSSE"
  ),
  ICC = c(
  icc_grp(df = df_ejss,
        cols1 = c("id","doi","num_hyp"),
        spread1 = c("id"),
        spread2 = "num_hyp",
        row1 = "doi"),
  icc_grp(df = df_jsams,
        cols1 = c("id","doi","num_hyp"),
        spread1 = c("id"),
        spread2 = "num_hyp",
        row1 = "doi"),
  icc_grp(df = df_msse,
        cols1 = c("id","doi","num_hyp"),
        spread1 = c("id"),
        spread2 = "num_hyp",
        row1 = "doi")
),
  Observations = c(
  irr_grp(df = df_ejss,
        cols1 = c("id","doi","num_hyp"),
        spread1 = c("id"),
        spread2 = "num_hyp",
        row1 = "doi")$subjects,
  irr_grp(df = df_jsams,
        cols1 = c("id","doi","num_hyp"),
        spread1 = c("id"),
        spread2 = "num_hyp",
        row1 = "doi")$subjects,
  irr_grp(df = df_msse,
        cols1 = c("id","doi","num_hyp"),
        spread1 = c("id"),
        spread2 = "num_hyp",
        row1 = "doi")$subjects
))
#df2 = df %>%
#  mutate(Tot = Kappa * Observations)
knitr::kable(df)
```



# Hypothesis Supported

```{r}

df_msse_2 = df_msse %>%
  filter(id != "Sena_Harlley")
  
df = data.frame(
  Journal = c(
    "EJSS",
    "JSAMS",
    "MSSE"
  ),
  Kappa = c(
  agree_na(df = df_ejss,
        cols1 = c("id","doi","di_sup"),
        spread1 = c("id"),
        spread2 = "di_sup",
        row1 = "doi")[[1]],
  agree_na(df = df_jsams,
        cols1 = c("id","doi","di_sup"),
        spread1 = c("id"),
        spread2 = "di_sup",
        row1 = "doi")[[1]],
  agree_na(df = df_msse,
        cols1 = c("id","doi","di_sup"),
        spread1 = c("id"),
        spread2 = "di_sup",
        row1 = "doi")[[1]]
),
  Observations = c(
  agree_na(df = df_ejss,
        cols1 = c("id","doi","di_sup"),
        spread1 = c("id"),
        spread2 = "di_sup",
        row1 = "doi")[[2]],
  agree_na(df = df_jsams,
        cols1 = c("id","doi","di_sup"),
        spread1 = c("id"),
        spread2 = "di_sup",
        row1 = "doi")[[2]],
  agree_na(df = df_msse,
        cols1 = c("id","doi","di_sup"),
        spread1 = c("id"),
        spread2 = "di_sup",
        row1 = "doi")[[2]]
))
df2 = df %>%
  mutate(Tot = Kappa * Observations)

knitr::kable(df)

#paste0("Overall Agreement: ",sum(df2$Tot)/sum(df2$Observations))
```

Overall Agreement: `r round(sum(df2$Tot)/sum(df2$Observations),4)*100`%

# Effect Size Reported

```{r }

df_msse_2 = df_msse %>%
  filter(id != "Sena_Harlley")


df = data.frame(
  Journal = c(
    "EJSS",
    "JSAMS",
    "MSSE"
  ),
  Kappa = c(
  agree_na(df = df_ejss,
        cols1 = c("id","doi","effect_size"),
        spread1 = c("id"),
        spread2 = "effect_size",
        row1 = "doi")[[1]],
  agree_na(df = df_jsams,
        cols1 = c("id","doi","effect_size"),
        spread1 = c("id"),
        spread2 = "effect_size",
        row1 = "doi")[[1]],
  agree_na(df = df_msse_2,
        cols1 = c("id","doi","effect_size"),
        spread1 = c("id"),
        spread2 = "effect_size",
        row1 = "doi")[[1]]
),
  Observations = c(
  agree_na(df = df_ejss,
        cols1 = c("id","doi","effect_size"),
        spread1 = c("id"),
        spread2 = "effect_size",
        row1 = "doi")[[2]],
  agree_na(df = df_jsams,
        cols1 = c("id","doi","effect_size"),
        spread1 = c("id"),
        spread2 = "effect_size",
        row1 = "doi")[[2]],
  agree_na(df = df_msse_2,
        cols1 = c("id","doi","effect_size"),
        spread1 = c("id"),
        spread2 = "effect_size",
        row1 = "doi")[[2]]
))
df2 = df %>%
  mutate(Tot = Kappa * Observations)
knitr::kable(df)

```

Overall Agreement: `r round(sum(df2$Tot)/sum(df2$Observations),4)*100`%

# Clinical Trial Status

Agreement on whether or not the study constitutes a clinical trial.

```{r }
df_msse_2 = df_msse %>%
  filter(id != "Sena_Harlley")

df = data.frame(
  Journal = c(
    "EJSS",
    "JSAMS",
    "MSSE"
  ),
  Kappa = c(
  agree_na(df = df_ejss,
        cols1 = c("id","doi","clin_trial"),
        spread1 = c("id"),
        spread2 = "clin_trial",
        row1 = "doi")[[1]],
  agree_na(df = df_jsams,
        cols1 = c("id","doi","clin_trial"),
        spread1 = c("id"),
        spread2 = "clin_trial",
        row1 = "doi")[[1]],
  agree_na(df = df_msse_2,
        cols1 = c("id","doi","clin_trial"),
        spread1 = c("id"),
        spread2 = "clin_trial",
        row1 = "doi")[[1]]
),
  Observations = c(
  agree_na(df = df_ejss,
        cols1 = c("id","doi","clin_trial"),
        spread1 = c("id"),
        spread2 = "clin_trial",
        row1 = "doi")[[2]],
  agree_na(df = df_jsams,
        cols1 = c("id","doi","clin_trial"),
        spread1 = c("id"),
        spread2 = "clin_trial",
        row1 = "doi")[[2]],
  agree_na(df = df_msse,
        cols1 = c("id","doi","clin_trial"),
        spread1 = c("id"),
        spread2 = "clin_trial",
        row1 = "doi")[[2]]
))
df2 = df %>%
  mutate(Tot = Kappa * Observations)
knitr::kable(df)

```
Overall Agreement: `r round(sum(df2$Tot)/sum(df2$Observations),4)*100`%

# Preregistration

Agreement on whether or not the study was preregistration.

```{r }
df_msse_2 = df_msse %>%
  filter(id != "Sena_Harlley")

df = data.frame(
  Journal = c(
    "EJSS",
    "JSAMS",
    "MSSE"
  ),
  Kappa = c(
  agree_na(df = df_ejss,
        cols1 = c("id","doi","prereg"),
        spread1 = c("id"),
        spread2 = "prereg",
        row1 = "doi")[[1]],
  agree_na(df = df_jsams,
        cols1 = c("id","doi","prereg"),
        spread1 = c("id"),
        spread2 = "prereg",
        row1 = "doi")[[1]],
  agree_na(df = df_msse_2,
        cols1 = c("id","doi","prereg"),
        spread1 = c("id"),
        spread2 = "prereg",
        row1 = "doi")[[1]]
),
  Observations = c(
  agree_na(df = df_ejss,
        cols1 = c("id","doi","prereg"),
        spread1 = c("id"),
        spread2 = "prereg",
        row1 = "doi")[[2]],
  agree_na(df = df_jsams,
        cols1 = c("id","doi","prereg"),
        spread1 = c("id"),
        spread2 = "prereg",
        row1 = "doi")[[2]],
  agree_na(df = df_msse,
        cols1 = c("id","doi","prereg"),
        spread1 = c("id"),
        spread2 = "prereg",
        row1 = "doi")[[2]]
))
df2 = df %>%
  mutate(Tot = Kappa * Observations)
knitr::kable(df)

```

Overall Agreement: `r round(sum(df2$Tot)/sum(df2$Observations),4)*100`%

# Data Statement

Agreement on whether or not the manuscript included a data statement. The confusion at JSAMS appears to be due that JSAMS requires a statement but this can be confused with a supplemental material section.

```{r }
df_msse_2 = df_msse %>%
  filter(id != "Sena_Harlley")

df = data.frame(
  Journal = c(
    "EJSS",
    "JSAMS",
    "MSSE"
  ),
  Kappa = c(
  agree_na(df = df_ejss,
        cols1 = c("id","doi","data_state"),
        spread1 = c("id"),
        spread2 = "data_state",
        row1 = "doi")[[1]],
  agree_na(df = df_jsams,
        cols1 = c("id","doi","data_state"),
        spread1 = c("id"),
        spread2 = "data_state",
        row1 = "doi")[[1]],
  agree_na(df = df_msse_2,
        cols1 = c("id","doi","data_state"),
        spread1 = c("id"),
        spread2 = "data_state",
        row1 = "doi")[[1]]
),
  Observations = c(
  agree_na(df = df_ejss,
        cols1 = c("id","doi","data_state"),
        spread1 = c("id"),
        spread2 = "data_state",
        row1 = "doi")[[2]],
  agree_na(df = df_jsams,
        cols1 = c("id","doi","data_state"),
        spread1 = c("id"),
        spread2 = "data_state",
        row1 = "doi")[[2]],
  agree_na(df = df_msse,
        cols1 = c("id","doi","data_state"),
        spread1 = c("id"),
        spread2 = "data_state",
        row1 = "doi")[[2]]
))
df2 = df %>%
  mutate(Tot = Kappa * Observations)
knitr::kable(df)

```

Overall Agreement: `r round(sum(df2$Tot)/sum(df2$Observations),4)*100`%

# Animal Study

Agreement on whether or not the study utilized animal models.


```{r }
df_msse_2 = df_msse %>%
  filter(id != "Sena_Harlley")

df = data.frame(
  Journal = c(
    "EJSS",
    "JSAMS",
    "MSSE"
  ),
  Kappa = c(
  agree_na(df = df_ejss,
        cols1 = c("id","doi","animal"),
        spread1 = c("id"),
        spread2 = "animal",
        row1 = "doi")[[1]],
  agree_na(df = df_jsams,
        cols1 = c("id","doi","animal"),
        spread1 = c("id"),
        spread2 = "animal",
        row1 = "doi")[[1]],
  agree_na(df = df_msse_2,
        cols1 = c("id","doi","animal"),
        spread1 = c("id"),
        spread2 = "animal",
        row1 = "doi")[[1]]
),
  Observations = c(
  agree_na(df = df_ejss,
        cols1 = c("id","doi","animal"),
        spread1 = c("id"),
        spread2 = "animal",
        row1 = "doi")[[2]],
  agree_na(df = df_jsams,
        cols1 = c("id","doi","animal"),
        spread1 = c("id"),
        spread2 = "animal",
        row1 = "doi")[[2]],
  agree_na(df = df_msse,
        cols1 = c("id","doi","animal"),
        spread1 = c("id"),
        spread2 = "animal",
        row1 = "doi")[[2]]
))
df2 = df %>%
  mutate(Tot = Kappa * Observations)
knitr::kable(df)

```

Overall Agreement: `r round(sum(df2$Tot)/sum(df2$Observations),4)*100`%

# RCT

Agreement on whether or not the study was a RCT.

```{r }
df_msse_2 = df_msse %>%
  filter(id != "Sena_Harlley")

df = data.frame(
  Journal = c(
    "EJSS",
    "JSAMS",
    "MSSE"
  ),
  Kappa = c(
  agree_na(df = df_ejss,
        cols1 = c("id","doi","RCT"),
        spread1 = c("id"),
        spread2 = "RCT",
        row1 = "doi")[[1]],
  agree_na(df = df_jsams,
        cols1 = c("id","doi","RCT"),
        spread1 = c("id"),
        spread2 = "RCT",
        row1 = "doi")[[1]],
  agree_na(df = df_msse_2,
        cols1 = c("id","doi","RCT"),
        spread1 = c("id"),
        spread2 = "RCT",
        row1 = "doi")[[1]]
),
  Observations = c(
  agree_na(df = df_ejss,
        cols1 = c("id","doi","RCT"),
        spread1 = c("id"),
        spread2 = "RCT",
        row1 = "doi")[[2]],
  agree_na(df = df_jsams,
        cols1 = c("id","doi","RCT"),
        spread1 = c("id"),
        spread2 = "RCT",
        row1 = "doi")[[2]],
  agree_na(df = df_msse,
        cols1 = c("id","doi","RCT"),
        spread1 = c("id"),
        spread2 = "RCT",
        row1 = "doi")[[2]]
))
df2 = df %>%
  mutate(Tot = Kappa * Observations)
knitr::kable(df)

```

Overall Agreement: `r round(sum(df2$Tot)/sum(df2$Observations),4)*100`%

# Significance Level

Agreement on whether or not the significance level was reported.

```{r }
df_msse_2 = df_msse %>%
  filter(id != "Sena_Harlley")

df = data.frame(
  Journal = c(
    "EJSS",
    "JSAMS",
    "MSSE"
  ),
  Kappa = c(
  agree_na(df = df_ejss,
        cols1 = c("id","doi","sig_level"),
        spread1 = c("id"),
        spread2 = "sig_level",
        row1 = "doi")[[1]],
  agree_na(df = df_jsams,
        cols1 = c("id","doi","sig_level"),
        spread1 = c("id"),
        spread2 = "sig_level",
        row1 = "doi")[[1]],
  agree_na(df = df_msse_2,
        cols1 = c("id","doi","sig_level"),
        spread1 = c("id"),
        spread2 = "sig_level",
        row1 = "doi")[[1]]
),
  Observations = c(
  agree_na(df = df_ejss,
        cols1 = c("id","doi","sig_level"),
        spread1 = c("id"),
        spread2 = "sig_level",
        row1 = "doi")[[2]],
  agree_na(df = df_jsams,
        cols1 = c("id","doi","sig_level"),
        spread1 = c("id"),
        spread2 = "sig_level",
        row1 = "doi")[[2]],
  agree_na(df = df_msse,
        cols1 = c("id","doi","sig_level"),
        spread1 = c("id"),
        spread2 = "sig_level",
        row1 = "doi")[[2]]
))
df2 = df %>%
  mutate(Tot = Kappa * Observations)
knitr::kable(df)

```

Overall Agreement: `r round(sum(df2$Tot)/sum(df2$Observations),4)*100`%

# Significance Test

Agreement on whether or not the manuscript reported a significance test.

```{r }
df_msse_2 = df_msse %>%
  filter(id != "Sena_Harlley")

df = data.frame(
  Journal = c(
    "EJSS",
    "JSAMS",
    "MSSE"
  ),
  Kappa = c(
  agree_na(df = df_ejss,
        cols1 = c("id","doi","sig_test"),
        spread1 = c("id"),
        spread2 = "sig_test",
        row1 = "doi")[[1]],
  agree_na(df = df_jsams,
        cols1 = c("id","doi","sig_test"),
        spread1 = c("id"),
        spread2 = "sig_test",
        row1 = "doi")[[1]],
  agree_na(df = df_msse_2,
        cols1 = c("id","doi","sig_test"),
        spread1 = c("id"),
        spread2 = "sig_test",
        row1 = "doi")[[1]]
),
  Observations = c(
  agree_na(df = df_ejss,
        cols1 = c("id","doi","sig_test"),
        spread1 = c("id"),
        spread2 = "sig_test",
        row1 = "doi")[[2]],
  agree_na(df = df_jsams,
        cols1 = c("id","doi","sig_test"),
        spread1 = c("id"),
        spread2 = "sig_test",
        row1 = "doi")[[2]],
  agree_na(df = df_msse,
        cols1 = c("id","doi","sig_test"),
        spread1 = c("id"),
        spread2 = "sig_test",
        row1 = "doi")[[2]]
))
df2 = df %>%
  mutate(Tot = Kappa * Observations)
knitr::kable(df)

```

Overall Agreement: `r round(sum(df2$Tot)/sum(df2$Observations),4)*100`%

# Result of Significance Test

Agreement on whether or not the study concluded a significant result

```{r }
df_msse_2 = df_msse %>%
  filter(id != "Sena_Harlley")

df = data.frame(
  Journal = c(
    "EJSS",
    "JSAMS",
    "MSSE"
  ),
  Kappa = c(
  agree_na(df = df_ejss,
        cols1 = c("id","doi","pval_sig"),
        spread1 = c("id"),
        spread2 = "pval_sig",
        row1 = "doi")[[1]],
  agree_na(df = df_jsams,
        cols1 = c("id","doi","pval_sig"),
        spread1 = c("id"),
        spread2 = "pval_sig",
        row1 = "doi")[[1]],
  agree_na(df = df_msse_2,
        cols1 = c("id","doi","pval_sig"),
        spread1 = c("id"),
        spread2 = "pval_sig",
        row1 = "doi")[[1]]
),
  Observations = c(
  agree_na(df = df_ejss,
        cols1 = c("id","doi","pval_sig"),
        spread1 = c("id"),
        spread2 = "pval_sig",
        row1 = "doi")[[2]],
  agree_na(df = df_jsams,
        cols1 = c("id","doi","pval_sig"),
        spread1 = c("id"),
        spread2 = "pval_sig",
        row1 = "doi")[[2]],
  agree_na(df = df_msse,
        cols1 = c("id","doi","pval_sig"),
        spread1 = c("id"),
        spread2 = "pval_sig",
        row1 = "doi")[[2]]
))
df2 = df %>%
  mutate(Tot = Kappa * Observations)
knitr::kable(df)

```


Overall Agreement: `r round(sum(df2$Tot)/sum(df2$Observations),4)*100`%

# Sample Size Justification

Agreement on whether or not the manuscript included a sample size justification.

```{r }
df_msse_2 = df_msse %>%
  filter(id != "Sena_Harlley")

df = data.frame(
  Journal = c(
    "EJSS",
    "JSAMS",
    "MSSE"
  ),
  Kappa = c(
  agree_na(df = df_ejss,
        cols1 = c("id","doi","N_just"),
        spread1 = c("id"),
        spread2 = "N_just",
        row1 = "doi")[[1]],
  agree_na(df = df_jsams,
        cols1 = c("id","doi","N_just"),
        spread1 = c("id"),
        spread2 = "N_just",
        row1 = "doi")[[1]],
  agree_na(df = df_msse_2,
        cols1 = c("id","doi","N_just"),
        spread1 = c("id"),
        spread2 = "N_just",
        row1 = "doi")[[1]]
),
  Observations = c(
  agree_na(df = df_ejss,
        cols1 = c("id","doi","N_just"),
        spread1 = c("id"),
        spread2 = "N_just",
        row1 = "doi")[[2]],
  agree_na(df = df_jsams,
        cols1 = c("id","doi","N_just"),
        spread1 = c("id"),
        spread2 = "N_just",
        row1 = "doi")[[2]],
  agree_na(df = df_msse,
        cols1 = c("id","doi","N_just"),
        spread1 = c("id"),
        spread2 = "N_just",
        row1 = "doi")[[2]]
))
df2 = df %>%
  mutate(Tot = Kappa * Observations)
knitr::kable(df)

```

Overall Agreement: `r round(sum(df2$Tot)/sum(df2$Observations),4)*100`%

# Reported Sample Size

Agreement on the reported sample size in each manuscript. One outlier removed from the JSAMS data set.

```{r}

df_jsams2 = df_jsams %>%
  filter(N < 10000)
df = data.frame(
  Journal = c(
    "EJSS",
    "JSAMS",
    "MSSE"
  ),
  ICC = c(
  icc_grp(df = df_ejss,
        cols1 = c("id","doi","N"),
        spread1 = c("id"),
        spread2 = "N",
        row1 = "doi"),
  icc_grp(df = df_jsams2,
        cols1 = c("id","doi","N"),
        spread1 = c("id"),
        spread2 = "N",
        row1 = "doi"),
  icc_grp(df = df_msse,
        cols1 = c("id","doi","N"),
        spread1 = c("id"),
        spread2 = "N",
        row1 = "doi")
),
  Observations = c(
  irr_grp(df = df_ejss,
        cols1 = c("id","doi","N"),
        spread1 = c("id"),
        spread2 = "N",
        row1 = "doi")$subjects,
  irr_grp(df = df_jsams,
        cols1 = c("id","doi","N"),
        spread1 = c("id"),
        spread2 = "N",
        row1 = "doi")$subjects,
  irr_grp(df = df_msse,
        cols1 = c("id","doi","N"),
        spread1 = c("id"),
        spread2 = "N",
        row1 = "doi")$subjects
))
#df2 = df %>%
#  mutate(Tot = Kappa * Observations)
knitr::kable(df)
```

Overall Agreement: `r round(sum(df2$Tot)/sum(df2$Observations),4)*100`%


